plots with prolactin

### 2019-12-14 analysis/16_PRL.Rmd
new plr and brca stuff

geneinfo <- read_csv("../metadata/00_geneinfo.csv") %>%  dplyr::select(Name, geneid, entrezid) %>% arrange(Name)
candidategenes <- c("PRL")
candidates.pit <- selectcandidatevsds(candidategenes, vsd.pit, colData.pit)

@@

p6 <- ggplot(candidates.pit, aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
  theme(legend.position = c(0.85,0.2), legend.direction = "horizontal") + 
  scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "PRL expression in the pituitary", x = "parental care stage") +
  annotation_custom(control, ymin = 12, ymax = 14, xmin = -7.8) +
  annotation_custom(bldg, ymin = 12, ymax = 14, xmin = -5.8) +
  annotation_custom(lay, ymin = 12, ymax = 14, xmin = -3.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = -1.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 0.6) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 2.4) +
  annotation_custom(hatch, ymin = 12, ymax = 14, xmin = 4.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 6.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 8.4)  + 
  ylim(c(13,24)) +
  guides(fill = FALSE, alpha = FALSE, color = guide_legend(order=1)) 
p6

@@

plot_grid(p5,p6,p7,p8)
```

>>>>

candidategenes <- c("PRL")
candidates.pit <- selectcandidatevsds(candidategenes, vsd.pit, colData.pit)

@@

@@

p6 <- ggplot(candidates.pit, aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
  theme(legend.position = c(0.85,0.2), legend.direction = "horizontal") + 
  scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
  labs(y = "PRL", x = NULL) +
  guides(fill = FALSE, alpha = FALSE, color = guide_legend(order=1)) +
  theme(axis.title.y  = element_text(face = "italic"))
p6

```{r PRLBRCA1}
brca <- c( "NP_989500.1")
brca.pit <- selectcBRCA1vsds(brca, vsd.pit, colData.pit)

meanBRCA <- brca.pit %>% 
    droplevels() %>% 
  dplyr::group_by(treatment) %>%
  dplyr::summarise(m = mean(BRCA1), 
                   se = sd(BRCA1)/sqrt(length(BRCA1))) %>%
  dplyr::mutate(m = round(m,1)) 
meanBRCA <- left_join(meanBRCA, birds)
meanBRCA$treatment <- factor(meanBRCA$treatment, levels = alllevels)
meanBRCA

brca1 <- brca.pit %>% 
  ggplot(aes(x = treatment, y = BRCA1, fill = treatment, color = sex)) +
    geom_boxplot() +
    theme_B3() +
  scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
  theme(legend.position = "none") + 
  labs(x = "increasing time >>", y = "BRCA1") +
  annotation_custom(control, ymin = 5, ymax = 5.5, xmin = -7.8) +
  annotation_custom(bldg, ymin = 5, ymax = 5.5, xmin = -5.8) +
  annotation_custom(lay, ymin = 5, ymax = 5.5, xmin = -3.8) +
  annotation_custom(inc, ymin = 5, ymax = 5.5, xmin = -1.8) +
  annotation_custom(inc, ymin = 5, ymax = 5.5, xmin = 0.6) +
  annotation_custom(inc, ymin = 5, ymax = 5.5, xmin = 2.4) +
  annotation_custom(hatch, ymin = 5, ymax = 5.5, xmin = 4.4) +
  annotation_custom(nestling, ymin = 5, ymax = 5.5, xmin = 6.4) +
  annotation_custom(nestling, ymin = 5, ymax = 5.5, xmin = 8.4) +
  ylim(5,8) +
  theme(axis.title.y  = element_text(face = "italic"))
brca1

plot_grid(p6, brca1, nrow = 2)
```
